Bullet Data Preparation for LIME Diagnostics Paper

### 2020-09-20 code/02-data-preparation.Rmd
added figure comparing rtrees predictions to our predictions

>>>>

Extracting the predictions on the training data from `rtrees` and using `rtrees` to make predictions on the filtered data:

```{r}
rtrees_pred = predict(bulletxtrctr::rtrees, type = "prob")[,2]
new_pred = predict(bulletxtrctr::rtrees, bullet_train_filtered %>% select(rownames(bulletxtrctr::rtrees$importance)), type = "prob")[,2]
```

Plot comparing the two predictions:

```{r}
data.frame(rtrees_pred = sort(rtrees_pred), new_pred = sort(new_pred)) %>%
  ggplot(aes(rtrees_pred, new_pred)) + 
  geom_point()
```
